Size-differentiated Export in Different Dynamical Regimes in the Ocean

### 2019-08-28 size_differentiated_export.tex
Updates from Overleaf

%\documentclass[]{article}

%\setlength{\parskip}{.5cm}
%\usepackage{natbib}
%\usepackage[table,xcdraw]{xcolor}
%\usepackage{graphicx}
%\usepackage{hyperref}
%\usepackage{amsmath}
%\usepackage{appendix}
%\usepackage[left=3cm,right=3cm]{geometry}
  % Apply watermark to document
%\usepackage{draftwatermark}
%\SetWatermarkLightness{0.9}
%\SetWatermarkScale{15}
%\SetWatermarkText{DRAFT}

@@

\begin{keypoints}
\item Submesoscale dynamics enhance the contribution of slow-sinking particles to POC export, especially for steep particle size-spectrum slopes
\item Remineralization processes intensify the role of slow-sinking particles, to the point where these particle sometime dominate POC export
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%
\begin{abstract}
Export of Particulate Organic Carbon (POC) is  mainly driven by gravitational sinking. Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux. However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles. Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) the ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope. The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important. The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export. A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles. Implementing a remineralization scheme generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven. Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export. This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux. 
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%
%\begin{article}

%\maketitle

\section{Introduction}

Photosynthesis in the sunlit upper ocean and the production of Particulate Organic Carbon (POC) takes up dissolved inorganic carbon and facilitates the uptake of CO$_2$ from the atmosphere. The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation.   %??? Removed 'long time scales', or define it
Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.

Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth. Particles produced through primary and secondary production in the surface layer that are relatively large and fast-sinking, tend to sink out of the upper surface layer 
%below the export depth   ?? remove this because we have not defined 'export depth'?? 
on timescales shorter than the timescale on which the particles get remineralized. It is reasonable to treat POC export as sinking-dominated if the vertical advective velocities in the ocean are weaker than the velocities associated with gravitational sinking. However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day. The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, which indicates $\mathcal{O}(10^8)$ greater abundance of small  particles than large particles. The biomass size spectrum, which indicates the distribution of biomass vs. particle size, tends to be flatter and variable in shape \citep{Sheldon72} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and varies, for example, between 2 and 3 depending on shape and porosity).  Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction. Even though the sinking velocity $w_s$ of particles does not perfectly relate to particle size $l$, it is fair to assume  that  $w_s \sim l^n$ (with $n=2$ according to Stokes law, and $1<n<2$ for complex particle shapes). Due to this, as well as the fact that particles of organic matter are not very much greater in their densities than seawater, a significant fraction of the biomass sinks very slowly (at velocities less than tens of meters per day).  When the gravitational sinking velocity of particles is comparable to (or smaller than) the vertical velocities in the flow field, the dynamics of the flow field can impact the trajectories and fate of the POC.  Thus, depending on the flow dynamics, and the fraction of slow-sinking particulate biomass, the sinking of organic matter can be affected by the fluid flow in the ocean.

Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.  For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016}.  
\cite{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic. Advectively subducting plumes or filaments of high oxygen, chlorophyll and small POC (evidenced through backscatter) were detected from a suite of gliders during the North Atlantic Bloom experiment \citep{Briggs_2011, Alkire_2012}. Using model simulations to capture the process of eddy-driven subduction, \cite{Omand_2015} estimated the downward advective flux of non-sinking POC and parameterized it. The flux of fast-sinking particles consisting largely of diatoms was observed from backscatter and quantified separately \citep{Briggs_2011}. But, the estimates did not simultaneously account for a range of sinking particle velocities.  Typically, particulate organic matter (POM) has a spectrum of sinking velocities and in order to understand its fate and export, we need to consider the biomass distribution as a function of the particle sinking velocity spectrum and its interaction with dynamics of the flow field in the ocean.

A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012,Mahadevan_2016}. Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2008,Klein_2009,McWilliams_2016}. In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}. Enhanced vertical velocities can generate a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2000,Levy_2001}, or can significantly increase the export of POC to the ocean interior through downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.  Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe these processes in-situ.

The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum. Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities.  However, despite progress on sampling and viewing particles in the ocean \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density. Depending on the fraction of  biomass in smaller particles (i.e., with slow sinking velocities), the impact of submesoscale dynamics on the export of POC is potentially significant.

%The impact of submesoscale dynamics on the net biomass flux depends on the sinking velocity spectrum (or size spectrum if we assume that sinking velocities are related to size). A relatively large fraction of the biomass at slow sinking velocities leads to a greater dependence of the biomass flux on the flow field, whereas the converse, leads to less dependence on the flow dynamics.

In this study, we account for a range of particle sinking velocities in a dynamic flow field. 
We  rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale. Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior. Particles are released in two fundamentally different flow fields in terms of dynamics based on observed conditions in the Northeast Pacific: In the summer, where ocean dynamics are characterized by low Rossby numbers and weak vertical advective velocities, and in the winter, where ocean dynamics include submesoscale frontal structures and local Rossby numbers $\mathcal{O}$(1). Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}. The impact of particles characteristics and ocean dynamics on the export of POC is quantified in Section \ref{sec: Results}, and discussed in Section \ref{sec: Discussion}. Section \ref{sec: Conclusions} summarizes the key conclusions of the study.

%A major pathway transferring carbon from the atmosphere to the ocean is through photosynthesis and the production of Particulate Organic Carbon (POC) in the upper ocean. Sinking POC then allows the transfer of organic carbon from the upper ocean to the interior, leading to carbon sequestration over long time scales \citep{Falkowski_1998}. Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.

%Traditionally, POC export is thought to be mainly driven by larger, faster-sinking, particles capable of gravitationally-sinking below the export depth on timescales shorter than the time scale on which the particles get remineralized. This is a reasonable assumption if one considers that vertical advective velocities in the ocean are generally much weaker than velocities associated with gravitational sinking. However, recent work demonstrates that the presence of mesoscale eddies can enhance carbon export through two main processes: First, by increasing primary productivity through the injection of nutrients into the euphotic layer, therefore increasing the particle concentration, logically leading to a greater export \citep{Levy_1998}. Second, by generating larger vertical velocities along the front located at the eddy perimeter \citep{vanHaren_2006, Waite_2016}. These studies demonstrate that ocean dynamics potentially play an important role in driving the carbon export from the euphotic layer to the ocean interior. This conclusion is further supported by a recent, yet large, body of literature focusing on ocean dynamics at submeso-scales (1-10 km) and the impact on biogeochemical processes \citep[see reviews in][]{Thomas_2008,Klein_2009,Mahadevan_2016}. Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{McWilliams_2016}. In this dynamical regime, geostrophic balance fails and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}. Just like at meso-scales, enhanced vertical velocities can generate either a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2012}, or can significantly increase the export of POC to the ocean interior \citep{Levy_2012, Estapa_2015,Omand_2015}.

%The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum. Through this mechanism, smaller particles can efficiently be exported over timescales shorter than their remineralization timescales, despite their slower sinking velocities. Considering the fact that, although containing less biomass per particle, smaller particles are far more numerous than larger particles, the impact of submesoscale dynamics on the export of POC is potentially significant. Submesoscale processes are, by definition, associated with spatial scales $\mathcal{O}$(1 km) and time scales $\mathcal{O}$(1 day), which makes it difficult to observe in-situ. Additionally, and despite recent methodological progress \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density.

%In this study, we therefore rely on a submesoscale-resolving non-hydrostatic model coupled with a particle-tracking module to explore the necessary conditions for slow-sinking particles to significantly contribute to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale. Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior. Particles are released in two fundamentally different flow fields in terms of dynamics based on observed conditions in the Northeast Pacific in the summer, where ocean dynamics are characterized by low Rossby numbers and weak vertical advective velocities, and in the winter, where ocean dynamics include submesoscale frontal structures and local Rossby numbers $\mathcal{O}$(1). Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}. The impact of particles characteristics and ocean dynamics on the export of POC is quantified in Section \ref{sec: Results}, and discussed in Section \ref{sec: Discussion}. Section \ref{sec: Conclusions} summarizes the key conclusions of the study.

@@

Time-varying wind stress and heat flux are prescribed at the surface boundary. Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory \citep{PMEL_data}. Daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long climatology. A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability. In all numerical experiments, simulations are 
run for the first 5 days without any forcing applied to the surface boundary. Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10. % (Figures \ref{fig: Papa_summer} and \ref{fig: Papa_winter}).
While the meriodional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling %that could contaminate the middle third of the model domain, where the analysis is focused 
(Figure \ref{fig: model_domain}a). A restoration timescale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b). While net surface heat fluxes are homogeneous in the zonal direction, a meridional gradient is maintained throughout the simulation. The meridional gradient was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}, and set to 1/24 W/m$^2$/km (Figure \ref{fig: model_domain}c).

@@

\subsubsection{Particle Advective Scheme}
To quantify the impact of submesoscale dynamics on the export of Particulate Organic Matter (POC), Lagrangian particle tracking is used in conjunction with the flow field obtained from the two experiments described above. Particles are tracked using the non-divergent velocity field at each face of a grid cell. The velocity field is then linearly interpolated onto the particle's position. For example, the eastward velocity (x-axis) of a particle is given by:

\begin{equation}
u(x) = u_{i-1} + \frac{(x - x_{i-1})}{(x_i - x_{i-1})}(u_{i}-u_{i-1})
\end{equation}
where the subscripts $i-1$ and $i$ denote the western and eastern walls of the grid cell where the particle is located, respectively. This can be re-written as:

\begin{equation}
\frac{\partial x}{\partial t} + \beta x + \delta =  0
\label{eq: eq_diff}
\end{equation}
where $\beta = (u_{i}-u_{i-1})/\Delta x$ and $\delta = -u_{i-1} - \beta x_{i-1}$ \citep{Doos_2013}. This differential equation can be solved analytically for $\beta \neq 0$:

\begin{equation}
x_{t_1} = \left(x_0 + \frac{\delta}{\beta}\right)\exp^{-\beta(t_1 - t_0)} - \frac{\delta}{\beta}
\label{eq: PT_advection}
\end{equation}
The time it will take for the particle to reach the eastern or western face of the grid cell can be computed by taking $x_{t_1} = x_i$ or $x_{t_1} = x_{i-1}$, respectively, and solving for $t_1$. For each advective timestep, the times required for the particle to reach any of the 6 walls of the grid cell are computed using (\ref{eq: PT_advection}). If any of those times is shorter than the advective timestep, the particle is advected until it reaches the cell wall. Then the flow field in the adjacent grid cell is considered and the particle is advected over the remaining time.

@@

For all particle-tracking experiments, a single particle seeding event is prescribed. In the horizontal, particles are seeded every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction. The seeding is centered over the mean position of the middle front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by undesired effects created by the solid north-south solid boundaries. In the vertical, particles are seeded every 1 m between 75 and 85 m. This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined by the 1\% light level. The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}. The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.

In each particle-tracking experiment, four different classes of particles are released. Each particle class is characterized by a different sinking velocity: 0.025, 0.05, 1, and 5 m/day. The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales. The fastest-sinking velocity is chosen as a low end-member representing velocity classes that will be exported in its entirety over the course of our experiment. The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.

The advective timestep for particles is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for three weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper that the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer. %The export horizon is therefore set to 100 m, based on the seasonal cycle observed at Station Papa \citep{Pelland_2016}.

\subsubsection{Density and Biomass Spectra}
\label{sec: equations_biomass}
The slope of the size spectrum of particles is traditionally described by the slope of the log-log curve, $\xi$, between particle number $N$ and particle radius $r$ \citep[also know as the Junge slope;][]{White_2015}:

\begin{equation}
N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}
\label{eq: powerlaw_radius}
\end{equation}
where $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily. For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically. Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}. %\cite{Bach_2012} also demonstrate that Stokes law is generally a lower-bound estimate of sinking velocities for a specific particle size. 
Assuming a Stokes-like relationship, we can construct a particle sinking velocity spectrum $N(w_s)$ based on (\ref{eq: powerlaw_radius}), where $w_{s_0}$ is the sinking speed of particles with a radius $r_0$:

>>>>

@@

\begin{keypoints}
\item Submesoscale dynamics enhance the contribution of slow-sinking particles to POC export, depending on their intensity and on the fraction of biomass in the slow sinking particle classes.
\item Remineralization processes can enhance the contribution of slow-sinking particles to the point where these particles sometimes dominate POC export
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%
\begin{abstract}
Export of Particulate Organic Carbon (POC) is  mainly driven by gravitational sinking. Thus, traditionally, it is thought that larger, faster-sinking particles make up most of the POC export flux. However, this need not be the case in a dynamic oceanic flow field, where the ocean velocity can influence the descent rate of particles. Particles with different settling speeds are released in two process-oriented model simulations of an upper ocean eddying flow to evaluate the impact of (1) ocean dynamics on the respective contribution of the different sinking-velocity classes to POC export, and (2) the particle number size-spectrum slope. The analysis reveals that the leading export mechanism changes from gravitationally-driven to advectively-driven as submesoscale dynamics become more important. The vertical velocity associated with submesoscale dynamics enhances the contribution of slower-sinking particles to POC export. A steeper particle size spectrum, also increases the relative contribution of smaller, slower-sinking particles. Implementing a remineralization scheme generally decreases the total amount of biomass exported, but its impact is weaker in dynamical regimes where submesoscale dynamics are present and export is advectively-driven. Under specific conditions, remineralization processes counter-intuitively enhance the role of slower-sinking particles to the point where these slower-sinking velocity classes dominate the export, therefore challenging the traditional paradigm for POC export. This study demonstrates that slow-sinking particles can be a significant contribution, and at times, even dominate the export flux. 
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%
\section{Introduction}

Photosynthesis in the sunlit upper ocean and the production of Particulate Organic Carbon (POC) takes up dissolved inorganic carbon and facilitates the uptake of CO$_2$ from the atmosphere. The sinking of POC exports organic carbon from the upper ocean to the interior, leading to the sequestration of carbon \citep{Falkowski_1998} on timescales ranging from days to years depending on the sinking depth and  circulation. Understanding the mechanisms driving the export of POC from the ocean's surface to the interior is therefore crucial to better constrain Earth's carbon budget.

Traditionally, POC export is thought to occur through gravitational sinking and one-dimensional models have been used to describe the sinking POC flux with depth. Particles produced through primary and secondary production in the surface layer that are relatively large and fast-sinking, tend to sink out of the upper surface layer on timescales shorter than the timescale on which the particles get remineralized. It is reasonable to treat POC export as sinking-dominated if the vertical advective velocities in the ocean are weaker than the velocities associated with gravitational sinking. However, Particulate Organic Matter (POM) has a wide range of particle shape, size and type, that result in particle sinking velocities ranging from practically zero, to several hundreds of meters per day. The size spectrum, or number distribution of particle sizes, is usually characterized by a power law with the power ranging between -2 and -4, for which the abundance of small particles is $\mathcal{O}(10^4 - 10^8)$ greater than large particles. The biomass size spectrum, which indicates the distribution of biomass vs. particle size, tends to be flatter and variable in shape \citep{Sheldon_1972} compared to the particle number spectrum, because the volume (and mass) of a particle scales with its linear size raised to a power that exceeds 1 (and typically varies between 2 and 3 depending on shape and porosity).  Importantly, it means that a significant fraction of the particulate biomass is in the small size fraction. Even though the sinking velocity $w_s$ of particles does not perfectly relate to particle size $l$, it is fair to assume  that  $w_s \sim l^n$ (with $n=2$ according to Stokes law, and $1<n<2$ for complex particle shapes). Due to this, as well as the fact that particles of organic matter are not very much greater in their densities than seawater, a significant fraction of the biomass sinks very slowly (at velocities less than tens of meters per day).  When the gravitational sinking velocity of particles is comparable to (or smaller than) the vertical velocities in the flow field, the dynamics of the flow field can impact the trajectories and fate of the POC.  Thus, depending on the flow dynamics, and the fraction of slow-sinking particulate biomass, the sinking of organic matter can be affected by the fluid flow in the ocean.

Recent studies have shown that ocean dynamics can play a role in driving the transport of carbon from the euphotic layer to the ocean interior.  For example, enhanced vertical velocities along the edge of a mesoscale eddy led to a funneling of particles along the eddy's periphery \citep{vanHaren_2006, Waite_2016}.  
\cite{Omand_2015}  found that submesoscale mixed layer eddies, while contributing to the restratification of a frontal zone, were subducting a large amount of non-sinking POC from the surface productive layer during the onset of the Spring bloom in the subpolar North Atlantic. Advectively subducting plumes or filaments of high oxygen, chlorophyll and small POC (evidenced through backscatter) were detected from a suite of gliders during the North Atlantic Bloom experiment \citep{Alkire_2012}. Using model simulations to capture the process of eddy-driven subduction, \cite{Omand_2015} estimated the downward advective flux of non-sinking POC and parameterized it. \cite{Briggs_2011} quantified the flux of fast-sinking particles consisting largely of diatoms from observations of optical backscatter. But, these estimates did not account for a range of sinking particle velocities.  Typically, particulate organic matter (POM) has a wide spectrum of sinking velocities and in order to understand its fate and export, we need to consider the biomass distribution as a function of the particle sinking velocity spectrum and its interaction with the dynamics of the flow field in the ocean.

A growing body of literature focusing on submesoscale (1-10 km) dynamics is exploring its impact on biogeochemical processes \citep{Levy_2012,Mahadevan_2016}. Submesoscale dynamics, characterized by Rossby numbers of order 1, typically develop in filaments in areas where sharp density fronts exist \citep{Thomas_2008,Klein_2009,McWilliams_2016}. In this dynamical regime, geostrophic balance breaks down and a secondary ageostrophic circulation develops across the front, capable of generating large vertical velocities on the order of 100 m/day \citep{FoxKemper_2008,Mahadevan_2016}. On the denser side of the front, the vorticity is cyclonic and associated with downwelling velocities, while anticyclonic vorticity and upwelling is expected on the lighter side of the front. The distribution of relative vorticity across a front is asymmetric and skewed toward cyclonic vorticity \citep{Rudnick_2001}, leading to more localized and more intense downwelling regions, as opposed to weaker and larger upwelling regions \citep{Mahadevan_2006}. Enhanced vertical velocities can generate a local bloom by supplying nutrients to the sunlit layer of the ocean \citep{Mahadevan_2000,Levy_2001}, or can significantly increase the export of POC to the ocean interior through downwelling \citep{Levy_2012, Gruber_2011,Estapa_2015,Omand_2015}.

The downwelling velocities $\mathcal{O}$(100 m/day) generated at submeso-scales provide a physical mechanism capable of competing with gravitational sinking and thus exporting particles over a larger portion of the particle size spectrum. Through this mechanism, smaller particles can be exported on timescales shorter than their remineralization timescales, despite their slower sinking velocities.   Depending on the fraction of  biomass in smaller particles (i.e., with slow sinking velocities), the impact of submesoscale dynamics on the export of POC is potentially significant.

In this study, we account for a range of particle sinking velocities in a dynamic flow field. Despite progress on sampling and viewing particles in the ocean \citep{McDonnell_2010}, direct measurements of particles sinking velocities are difficult to obtain, and often inferred from key parameters such as particle type, size, and density. Though we acknowledge a large variability in these relationships, we assume a relationship between particle size, biomass, and particle sinking velocity in order to assess the impact of the flow dynamics and particle size spectrum on the export flux.

We  rely on a submesoscale-resolving, non-hydrostatic ocean model to simulate the dynamics in the upper few hundred meters of the ocean. The model does not represent surface waves or boundary layer turbulence, but rather, examines the fate of particulate organic matter beneath the turbulent surface boundary layer.
The dynamical model is coupled with a particle-tracking module to model the advection of particles by fluid flow, while neglecting the effects of particle inertia and drag on their advection. In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$).

The model is used to quantify the contribution of slow-sinking particles to carbon export, as a function of (1) the dynamics of the flow field, (2) the slope of the sinking velocity spectrum, and (3) the remineralization timescale. Particles in the model are prescribed with both a constant and time-varying sinking velocity to mimic a remineralizing behavior. Particles are released in two fundamentally different flow fields in terms of dynamics based on observed conditions in the Northeast Pacific: In the summer, where ocean dynamics are characterized by low Rossby numbers and weak vertical advective velocities, and in the winter, where ocean dynamics include submesoscale frontal structures and local Rossby numbers $\mathcal{O}$(1). Both simulations and the particle-tracking module are described in Section \ref{sec: Methods}. The impact of particles characteristics and ocean dynamics on the export of POC is quantified in Section \ref{sec: Results}, and discussed in Section \ref{sec: Discussion}. Section \ref{sec: Conclusions} summarizes the key conclusions of the study.

@@

Time-varying wind stress and heat flux are prescribed at the surface boundary. Time series are computed from measurements collected at Station Papa and available through the Pacific Marine Environmental Laboratory \citep{PMEL_data}. Daily wind stress and net heat fluxes are calculated over the period 2007-2016 to produce a year-long climatology. A squared low-pass filter with a cut-off frequency of 8.5 days is applied to both time series to remove high-frequency variability. In all numerical experiments, simulations are 
run for the first 5 days without any forcing applied to the surface boundary. Surface wind stress and heat fluxes are then linearly ramped up between days 5 and 10 of the simulation, to reach realistic values at day 10.

While the meridional component, $\tau_y$, is set to zero, the zonal component of the wind stress, $\tau_x$, is prescribed at the surface throughout the model domain and is tapered at the northern and southern boundaries to avoid excessive Ekman-driven upwelling and downwelling (Figure \ref{fig: model_domain}a). A restoration timescale is prescribed to contain the curl-driven upwelling and downwelling regions generated by the tapering of the wind stress, as well as to limit internal wave reflection at the solid boundaries back into the domain (Figure \ref{fig: model_domain}b). While net surface heat fluxes are homogeneous in the zonal direction, a meridional gradient is maintained throughout the simulation. The meridional gradient was determined from the North American Regional Reanalysis (NARR) product \citep{Mesinger_2006}, and set to 1/24 W/m$^2$/km (Figure \ref{fig: model_domain}c).

@@

\subsubsection{Particle Advective Scheme}
To quantify the impact of submesoscale dynamics on the export of Particulate Organic Matter (POC), Lagrangian particle trajectories are computed using the same scheme as in ``TRACMASS'' \citep{Doos_2013} with the flow fields from the two experiments described above. The three-dimensional, non-divergent velocity components from the faces of each ``C" grid cell are linearly interpolated onto the particle's position within the grid cell. For example, the eastward (along the x-axis) velocity  of a particle is given by
\begin{equation}
u(x) = u_{i-1} + \frac{(x - x_{i-1})}{(x_i - x_{i-1})}(u_{i}-u_{i-1}),
\end{equation}
where the subscripts $i-1$ and $i$ denote the western and eastern walls of the grid cell where the particle is located, respectively. This can be re-written as
\begin{equation}
\frac{\partial x}{\partial t} + \beta x + \delta =  0,
\label{eq: eq_diff}
\end{equation}
where $\beta = (u_{i}-u_{i-1})/\Delta x$ and $\delta = -u_{i-1} - \beta x_{i-1}$ \citep{Doos_2013}. This differential equation can be solved analytically for $\beta \neq 0$ as
\begin{equation}
x_{t_1} = \left(x_0 + \frac{\delta}{\beta}\right)\exp^{-\beta(t_1 - t_0)} - \frac{\delta}{\beta}
\label{eq: PT_advection}
\end{equation}
The time it will take for the particle to reach the eastern or western face of the grid cell can be computed by taking $x_{t_1} = x_i$ or $x_{t_1} = x_{i-1}$, respectively, and solving for $t_1$. For each advective timestep, the times required for the particle to reach any of the 6 walls of the grid cell are computed using (\ref{eq: PT_advection}). If any of those times is shorter than the advective timestep, the particle is advected until it reaches the cell wall. Then the flow field in the adjacent grid cell is considered and the particle is advected over the remaining time.

@@

For all particle-tracking experiments, a single particle seeding event is prescribed. In the horizontal, particles are seeded every 250 m over the entire domain in the x-direction, and for 100 $<y<$ 200 km in the y-direction. The seeding is centered over the mean position of the central front (see Figure \ref{fig: Papa_summer}) and is therefore not affected by undesired effects created by the solid north-south solid boundaries. In the vertical, particles are seeded every 1 m between 75 and 85 m. This depth range is chosen as it corresponds to the average euphotic depth at Station Papa, defined by the 1\% light level. The euphotic depth was computed for the months of February and June over the period 2007-2016 from profiles of Photosynthetically Available Radiation (PAR) collected at Station Papa as part of the long-term monitoring of Line P executed by the Department of Fisheries and Ocean Canada\footnote{https://www.waterproperties.ca/linep/index.php}. The average euphotic depth computed for both of these months is around 80 m, which agrees with previously established estimates of the euphotic depth \citep{Sherry_1999,Harrison_2004}.

In each particle-tracking experiment, four different classes of particles are released. Each particle class is characterized by a different sinking velocity: 0.025, 0.05, 1, and 5 m/day. The slowest-sinking class is essentially selected to represent non-sinking particles: based on the setup of our experiments, the slowest-sinking particles would take 800 days on average to be exported to a depth of 100 m through gravitational sinking, a timescale much greater than commonly observed remineralization timescales. The fastest-sinking velocity is chosen as an end-member velocity class of particle that will be exported in its entirety over the course of our experiment. %The results presented for the 5 m/day sinking class can therefore be extrapolated to any class with a higher sinking velocity.

The advective timestep for particles is set to 1.5 hours. The flow field is linearly interpolated in time between model outputs, justifying the higher temporal resolution used for particle tracking in \textit{Papa\_winter}. Particle positions are saved every 3 hours, along with key model variables interpolated onto the particle positions (e.g., density, vorticity). Particles are tracked for three weeks (28 days). Each particle-tracking experiment contains 1,971,717 particles per sinking-velocity class, for a total of 9,858,585 particles. Particles located deeper than the maximum winter mixed layer \citep[i.e., 100 m;][]{Pelland_2016, Plant_2016} are considered exported, as they will likely not be re-entrained into the mixed layer.

\subsubsection{Density and Biomass Spectra}
\label{sec: equations_biomass}
The slope $\xi$ of the size spectrum of particles \citep[also know as the Junge slope;][]{White_2015} is the slope of the log-log curve of particle number $N$ vs. particle radius $r$, where
\begin{equation}
N(r) = N_0 \left(\frac{r}{r_0}\right)^{-\xi}.
\label{eq: powerlaw_radius}
\end{equation}
Here, $N_0$ and $r_0$ represent a reference particle number and radius, chosen arbitrarily. For small particles ($<$400 $\mu$m) and relatively low temperature ($<$15$^o$C), it has been shown that the relationship between particle radius $r$ and sinking velocity $w_s$ exhibits a range of variation and is difficult to determine empirically. Nevertheless, Stokes' law, where $w_s \propto r^2$, is often used as a lower-bound sinking velocity estimate \citep{Bach_2012}.
